Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-09 manuscript/tables&figures.Rmd
update table 1 with final results

\blandscape
```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/publication/table1_hypothesis_table3.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  pack_rows("Tree size and microenvironment", 1, 6, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
 pack_rows("Across the forest vertical profile, taller trees are exposed to higher evaporative demand.", 1, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("At least within the forest setting, taller trees are less drought tolerance.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower drought tolerance.", 6, 6, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 7, 11, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf drought tolerance traits--predict drought tolerance.", 7, 11, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", " ", "tree-ring drought records" = 3, " ")) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(2, width = "1.7cm")  %>%
  column_spec(3:5, width = "1.2cm") %>%
  column_spec(6, width = "1.8cm") 
 # kableExtra::landscape()
```

Parentheses indicate that the prediction was supported by one but not all of the top  models (Table S6). Dash symbols indicate that the response was not significant (Table S4), or not represented in any of the top models (Table S6).

>>>>

\blandscape
```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/publication/table1_hypothesis_table3.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  pack_rows("Tree size and microenvironment", 1, 6, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
 pack_rows("Across the forest vertical profile, taller trees are exposed to higher evaporative demand.", 1, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("At least within the forest setting, taller trees are less drought tolerant.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower drought tolerance.", 6, 6, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 7, 11, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf drought tolerance traits--predict drought tolerance.", 7, 11, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", " ", "tree-ring drought records" = 3, " ")) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(2, width = "1.7cm")  %>%
  column_spec(3:5, width = "1.2cm") %>%
  column_spec(6, width = "1.8cm") 
 # kableExtra::landscape()
```

Parentheses indicate that the prediction was supported by at least one but not all of the top  models (Table S6). Dash symbols indicate that the response was not significant (Table S4), or not represented in any of the top models (Table S6).
